---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$ regchg_i = \beta_0 _{t,i} + \beta_1 local_{t,i} + \beta_2 poverty_{pn,i} + \beta_3 local_{t,i} * poverty_{pn,i} + \epsilon_i$$

* Describe the population for which you are creating the model.

The population is individuals in 1,674 communities in Kenya in 2013.

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.
```{r}
fit <- stan_glm(reg_chg ~ treatment + poverty_n + treatment * poverty_n,
                data = week_9,
                refresh = 0)

print(fit, details = FALSE, digits = 10)

# OR R will just fill in so you can just put 
# fit <- stan_glm(reg_chg ~ treatment * poverty_n,
#                 data = week_9,
#                 refresh = 0)

# For the interaction of treatment local and poverty_n we see a 0.0154260059
# increase in voter registration compared to a 0.0210029449 increase for local
# alone,0.0026621776 for poverty alone, and 0.0043596025 for treatment control
# alone.
```

## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

The Kenya dataset gives us the data necessary to answer the question.     

* Describe the ideal Preceptor Table.

The ideal Preceptor Table would have local and control treatment outcomes for each individual and include other variable that may impact the population including the polling station, poverty, etc.  

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.
```{r}
fit <- stan_glm(reg_chg ~ treatment + poverty_n + treatment * poverty_n,
                data = week_9,
                refresh = 0)

new_obs <- tibble(treatment = "local",
                  poverty_n = -1.60835093)

pp <- posterior_predict(fit, 
                        new_data = new_obs) %>%
  as_tibble() %>%
  mutate_all(as.numeric)

pp

pp %>%
  ggplot(aes(x = `1`,
             y = after_stat(count/sum(count)))) +
  geom_histogram(fill = "blue", color = "white", alpha = 0.5, bins = 100) +
  labs(title = "Posterior Density Distribution for Polling Station 007/001",
         subtitle = 
         "Average treatment effect on voter registration",
         x = "Average Voter Registration Change",
         y = "Probability") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  geom_vline(xintercept = 0.04)

sum(pp$`1` > 0.04)/length(pp$`1`)

```

* Answer the President's question.

 


## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 



